Scikit-learn: API design for machine learning

### 2013-06-17 paper.tex
wordings

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning (this is the role of the \texttt{fit} method,
see below).  Its only goal is to set the parameter values and freeze the
behavior of the estimator.
Initializing and fitting an estimator object
proceeds in a way that is similar to partial function application:
an estimator can be considered a function
that maps hyperparameter settings to an actual learning algorithm.
The advantage of this API
over one where the object initializer would perform the learning
will become especially apparent in Section~\ref{sec:advanced-api}.

@@

Additionally, by leveraging that fact that \texttt{fit}
always returns the estimator it was called on,
the \texttt{StandardScaler} example above
can be rewritten in a single line using a ``method chaining'' style:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}
Finally, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, clustering algorithms provide a
\texttt{fit\_predict} method
that is equivalent to \texttt{fit} followed by \texttt{predict},
and thus returns the cluster labels assigned to the training data samples.

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning (this is the role of the \texttt{fit} method,
see below).  Its only goal is to set the parameter values and freeze the
behavior of the estimator.
Initializing and fitting an estimator object proceeds in a way that is similar
to partial function application: an estimator can be considered as a function
that maps hyper-parameter settings to an actual learning algorithm. The
advantage of this API over one where the object initializer would perform the
learning will become especially apparent in Section~\ref{sec:advanced-api}.

@@

Additionally, by leveraging the fact that \texttt{fit} always returns the
estimator it was called on, the \texttt{StandardScaler} example above can be
rewritten in a single line using method chaining:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}
Finally, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, clustering algorithms provide a
\texttt{fit\_predict} method
that is equivalent to \texttt{fit} followed by \texttt{predict},
and thus returns the cluster labels assigned to the training data samples.
